PyPy's Approach to Virtual Machine Construction

### 2006-05-31 talk/dls2006/paper.tex
Tentative categories.

@@

\begin{figure}
\begin{verbatim}
def ll_append(lst, newitem):
  # Append an item to the end of the vector.
  index = lst.length       # get the 'length' field
  ll_resize(lst, index+1)  # call another helper
  itemsarray = lst.items   # get the 'items' field
  itemsarray[index] = item # behaves like a C array
\end{verbatim}
\caption{a helper to implement \texttt{list.append()}.}
\label{fig_llappend}
\end{figure}

>>>>

\category{D.3.4}{Programming Languages}{Processors}[code generation,
interpreters, run-time environments]
\category{F.3.2}{Logics and Meanings of Programs}{Semantics of Programming
Languages}[program analysis]

@@

\begin{figure}
\begin{verbatim}
def ll_append(lst, newitem):
  # Append an item to the end of the vector.
  index = lst.length       #get the 'length' field
  ll_resize(lst, index+1)  #call another helper
  itemsarray = lst.items   #get the 'items' field
  itemsarray[index] = item #behaves like a C array
\end{verbatim}
\caption{a helper to implement \texttt{list.append()}.}
\label{fig_llappend}
\end{figure}
